A generalized definition of multidimensional item response theory parameters

### 2024-03-29 output/paper_draft/paper_M2PLM_parameters.Rmd
Corrects "Polar coordinatess" section
The deleted content was redundant with Proposition 1

From Proposition 1,
any trait vector $`r TRAIT_VECTOR`$ is expressed in polar coordinates as

\begin{equation}
  `r TRAIT_VECTOR_POLAR_EQ`.                      (\#eq:trait-equivalence-polar)
\end{equation}

Thus, the `r MODEL_ACRONYM` model is expressed in polar coordinates as

>>>>

Applying Proposition 1 to the model formulation in \@ref(eq:M2PL-formulation),
the `r MODEL_ACRONYM` model is expressed in polar coordinates as
